### 2012-11-25 paper.tex

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure  Class \\ \midrule   
               &  0.649   & 0.263   & 0.648     & 0.649  & 0.648      1     \\    
               &  0.402   & 0.13    & 0.475     & 0.402  & 0.436      2     \\        
               &  0.548   & 0.292   & 0.499     & 0.548  & 0.522      3     \\    
Weighted Avg.  &  0.558   & 0.243   & 0.557     & 0.558  & 0.557            \\ \bottomrule 
    \end{tabular*}
\caption{Decision Tree on Contraceptive Data Set -- using binary splits} 
\label{tab:contra:dec:bin}
\end{table*}
\FloatBarrier

>>>>

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure &  Class \\ \midrule   
               &  0.649   & 0.263   & 0.648     & 0.649  & 0.648     &  1     \\    
               &  0.402   & 0.13    & 0.475     & 0.402  & 0.436     &  2     \\        
               &  0.548   & 0.292   & 0.499     & 0.548  & 0.522     &  3     \\    
Weighted Avg.  &  0.558   & 0.243   & 0.557     & 0.558  & 0.557     &        \\ \bottomrule 
    \end{tabular*}
\caption{Decision Tree on Contraceptive Data Set -- using binary splits} 
\label{tab:contra:dec:bin}
\end{table*}
\FloatBarrier

\subsection{Random Forest}
Random Forests perform even worse than the J48 with default settings. We can see in table \ref{tab:contra:rand:default} that only the half of all classified instances are classified correctly.

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure  & Class  \\  \midrule      
               &  0.631   & 0.328   & 0.589     & 0.631  & 0.609      & 1      \\       
               &  0.36    & 0.16    & 0.397     & 0.36   & 0.378      & 2      \\       
               &  0.456   & 0.274   & 0.469     & 0.456  & 0.462      & 3      \\       
Weighted Avg.  &  0.509   & 0.271   & 0.504     & 0.509  & 0.506      &        \\  \bottomrule     
    \end{tabular*}
\caption{Random Forests on Contraceptive Data Set -- Default Settings} 
\label{tab:contra:rand:default}
\end{table*}
\FloatBarrier

\paragraph{More but shorter trees}
Random forests perform best on the data set with a maximum depth of 5 branches. After this improvement we can lift the precision up to 54.4\%. Furthermore, our random forest benefits from adding five more random trees so we can enhance the precision to  54.7\%.
\paragraph{More Features}
The most significant improvement can then observed after increasing the number of randomly chosen features. By default, the number of chosen features for this data set lays about 4 ( $ log_2(10) + 1 $ ). Choosing two more of them results in the best accuracy for random forests on this data set, as shown in table \ref{tab:contra:rand:6f}.

\begin{table*}[htb]\centering
  \begin{tabular*}{\columnwidth}{@{}lllllll@{}}
      \toprule 
      \multicolumn{7}{c}{Detailed Accuracy By Class} \\ 
               &  TP Rate & FP Rate & Precision & Recall & F-Measure &  Class \\  \midrule     
               &  0.604   & 0.231   & 0.661     & 0.604  & 0.631     &  1     \\  
               &  0.408   & 0.127   & 0.484     & 0.408  & 0.443     &  2     \\  
               &  0.593   & 0.326   & 0.491     & 0.593  & 0.537     &  3     \\  
Weighted Avg.  &  0.556   & 0.241   & 0.562     & 0.556  & 0.556     &        \\  \bottomrule 
    \end{tabular*}
\caption{Random Forests on Contraceptive Data Set -- with at least 6 chosen features} 
\label{tab:contra:rand:6f}
\end{table*}
\FloatBarrier
